`Total-evidence' Bayesian estimation of phylogeny, divergence times and fossil ages

### 2016-05-03 fossilDating-revision.tex
added CCE affiliation

\noindent {\normalsize \sc  Alexei J.\ Drummond$^{1,2}$ and Tanja Stadler$^{2,3}$}\\
\noindent {\small \it 
$^1$Department of Computer Science, University of Auckland, Auckland, 1010, New Zealand;\\
$^2$Department of Biosystems Science \& Engineering, Eidgen\"{o}ssische Technische Hochschule Z\"{u}rich, 4058 Basel, Switzerland;\\
$^3$Swiss Institute of Bioinformatics (SIB), Switzerland.}
\end{center}
\medskip
\noindent{\bf Corresponding author:} Alexei J. Drummond, Department of Computer Science, University of 
Auckland, 38 Princes Street, Auckland, 1010, New Zealand; E-mail: alexei@cs.auckland.ac.nz\\

>>>>

\noindent {\normalsize \sc  Alexei J.\ Drummond$^{1,2,3}$ and Tanja Stadler$^{3,4}$}\\
\noindent {\small \it 
$^1$Centre for Computational Evolution, University of Auckland, Auckland, New Zealand;\\
$^2$Department of Computer Science, University of Auckland, Auckland, 1010, New Zealand;\\
$^3$Department of Biosystems Science \& Engineering, Eidgen\"{o}ssische Technische Hochschule Z\"{u}rich, 4058 Basel, Switzerland;\\
$^4$Swiss Institute of Bioinformatics (SIB), Switzerland.}
\end{center}
\medskip
\noindent{\bf Corresponding author:} Alexei J. Drummond, Centre for Computational Evolution, University of 
Auckland, Auckland, New Zealand; E-mail: alexei@cs.auckland.ac.nz\\
